The Astropy Project

### 2017-11-12 main.tex
tables

The \package{Tables} package provides wrappers to \package{NumPy} structure arrays, which can contain heterogeneous data sets.   The package was described in detail in \cite{astropy}. Tables now has the ability to work with other astropy classes including Quantities, Time, and Coordinates.  In addition, operations can also be performed on Tables.

%QTable is new, mixin columns for time and coordinates. Table operations were added in v0.3

>>>>

The \package{astropy.table} package provides wrappers to \package{numpy} structure arrays, which can contain heterogeneous data sets. The package was described in detail in \cite{astropy}. Tables now has the ability to work with other \astropypkg classes including \texttt{Quantity}, \texttt{Time}, and \texttt{SkyCoord}. In addition, operations can also be performed on Tables.

We summarize key new features or updates to \package{astropy.table} below.
%QTable is new, mixin columns for time and coordinates. Table operations were added in v0.3

\inlinecomment{Adrian PW}{The new features below need filling in.}

\begin{description}
    \item[QTable] TODO...quantity tables
    \item[Mixin columns for time and coordinates] TODO...
\end{description}
